Formalizing Stack Safety as a Security Property

### 2022-08-24 submission5/onlyformalism.tex
Emergency push as laptop makes nasty fan noises

The set of instructions, \(I\), contains the RISC-V ISA. We further introduce a set
a set \(J\) of {\it overlay sequences}: sequences of instructions that operate as if
they were single, atomic pseudoinstructions in a larger machine.

execute atomically
via a special {\it overlay step} and which carry additional source-level information
that designates their purpose, and which therefore comes with security obligations.
An overlay sequence has two parts, a {\it pseudo-instruction} drawn from those

There is additionally a set
of macro-instructions \(J\), described in detail in Figure \ref{fig:macros}.
Every macro-instruction \(j \in J\) has a
size \(\mathit{size}(j)\) and can be decomposed into a sequence of fragments
\(j_0 \dots j_{\mathit{size}(J)}\), where \(j_n \in J^*\).
The partial function \(\mathit{decode} : \WORDS \rightharpoonup I + J^*\) may decode a value
into either an instruction or a macro-instruction fragment.

\begin{figure}
  \begin{tabular}{| l | l l |}
    \hline
    Macro & \multicolumn{2}{|l|}{Parameters} \\
    \hline
    \multirow{3}{*}{\(\mathbf{call}\)}
    & \(\reg\) & Register containing destination \\
    & \(tr\) & Type record \\
    & \(pubs\) & Public set \\
    \hline
    \multirow{3}{*}{\(\mathbf{tailcall}\)}
    & \(\reg\) & Register containing destination \\
    & \(tr\) & Type record \\
    & \(pubs\) & Public set \\
    \hline
    \multirow{2}{*}{\(\mathbf{enter}\)}
    & \(tr\) & Type record \\
    & \(n\) & Size of locals \\
    \hline
    \(\mathbf{return}\)
    & \(pubs\) & Public set \\
    \hline
    \(\mathbf{yield}\) & & \\
    \(\mathbf{setex}\) & & \\
    \(\mathbf{throwex}\) & & \\
    \hline
  \end{tabular}
  \caption{Macro-instructions}
  \label{fig:macros}
\end{figure}

>>>>

The set of instructions, \(I\), contains the RISC-V ISA. We further introduce a set
a set \(J\) of {\it overlay sequences}: sequences of instructions that operate as if
they were single, atomic pseudoinstructions. Overlay sequences are {\it calls},
{\it returns}, {\it tailcalls}, exception {\it catches} and {\it throws},
and object {\it allocs}, and each carries a sequence of instructions
that implements the operation. When

\begin{figure}
  \begin{tabular}{| l | l l |}
    \hline
    Macro & \multicolumn{2}{|l|}{Parameters} \\
    \hline
    \multirow{3}{*}{\(\mathbf{call}\)}
    & \(\reg\) & Register containing destination \\
    & \(tr\) & Type record \\
    \hline
    \multirow{3}{*}{\(\mathbf{tailcall}\)}
    & \(\reg\) & Register containing destination \\
    & \(tr\) & Type record \\
    \hline
    \multirow{2}{*}{\(\mathbf{enter}\)}
    & \(tr\) & Type record \\
    \hline
    \(\mathbf{return}\)
    & \(pubs\) & Public set \\
    \hline
    \(\mathbf{yield}\) & & \\
    \(\mathbf{setex}\) & & \\
    \(\mathbf{throwex}\) & & \\
    \hline
  \end{tabular}
  \caption{Macro-instructions}
  \label{fig:macros}
\end{figure}
